Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-22 draft/Results.tex
images and stuff

The system has two main parts the DPSO stroke segmentation and symbol recognition. Each part is evaluated separately. The preprocessing procedures and computation is evaluated using their effect on the segmentation algorithm. These results are reported in section \ref{sec:ResultsDetails}. The effect of number of agents, the error thresholds and various other PSO parameters are investigated in Section \ref{sec:PSO}. %The results presented in Section \ref{sec:ResultsDetails} and \ref{sec:PSO}.

@@

	\caption{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}
\begin{table}
\begin{center}
\scalebox{0.9}{
 \begin{tabular}{|p{5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
 \hline
 & Hs-DB &  EL-DB & LD-DB \\ \hline
No of samples  &  7791 & 2764 & 1859 \\ \hline
No of categories  & 13 & 15 & 8 \\ \hline
Avg. Samples per Category& 600 & 184 & 232 \\\hline 
No of users  & 16 & 7 & 7 \\  \hline
Balanced & Yes&No & No \\ \hline
Splits  & 5 random splits  & 5 random splits  & 5 random splits  \\ \hline
Examples & Figure \ref{fig:symbolSet}  & Figure \ref{fig:ElectSet}  & Figure \ref{fig:LogicSet}   \\ \hline
\end{tabular}
}
\caption[Datasets Comparisons]{Datasets Comparisons} 
\label{tab:datasets}

@@

 The effect of number of agents, the error thresholds and various other parameters was investigated. The result of these tests are shown in Figure \ref{fig:swarmtesting} and \ref{fig:swarmtesting2}. Figure \ref{fig:swarmtesting} shows that as the number of agents increase the \textit{Segmentation Error} value decrease. Similar results for the maximum swarm iterations are shown in Figure \ref{fig:swarmtesting}.  Other algorithm parameters like $c_1$,$c_2$ that were mentioned in Section\ref{sec:ParticleSwarmAlgorithm} are tested using similar tests (Figure \ref{fig:swarmparamterw.jpg} and \ref{fig:swarmtesting2}). The final values are for maximum number of iteration = 80 with 15 particles. The final number of agents and maximum swarm iteration used in the system was based trade off between errors achieved versus the computation time.

 \begin{figure}
	\centering		
	 \includegraphics[scale=0.5]{paperImages/swarmAgentTest.jpg.eps}
	 	\caption{Segmentation Error Vs. Number of agents}
	 	\label{fig:swarmtesting}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

@@

 The effects of symbol complexity in a dataset were testing in the following experiment. These experiments test how many samples will be required to finally obtain good performance from the recognizer system. In the following experiments, we tested the system using different number of sample per category. 
 Figure \ref{fig:Alg1Ds} and \ref{fig:Alg2Ds} shows that Hs-DB requires more number of sample for training to achieve same result as in other data sets. This is due that it contains less signal and conceptual variation that the other two datasets. Figure \ref{fig:samplesofHS-DB.jpg} shows sample of data collected from one user in Hs-Db it is clear that it has reasonable amount of variation between users but it is limited. Recognizing symbols that contains high variation in drawing style using fewer symbols in training prove the efficiency of our system.
 \begin{figure}
	\centering
		\includegraphics{results/Alg1Ds.eps}
	\caption{AlgS1 on different datasets}
	\label{fig:Alg1Ds}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/Alg2Ds.eps}
	\caption{AlgS2 on different Datasets }
	\label{fig:Alg2Ds}
\end{figure}
 \begin{figure}
	\centering
	\includegraphics[scale=0.5]{results/samplesofHS-DB.jpg.eps}
	\caption{Hs-DB shapes drawn by single user}
	\label{fig:samplesofHS-DB.jpg}
\end{figure}
  Figure \ref{fig:correct2.jpg} shows examples of correctly recognized symbol using our system. The figure shows that system recognized some hard to recognize example in both EL-DB and DL-DB. An example of symbols that was not correctly recognized are in Figure \ref{fig:erros}. Most of the wrong classifications were due to how messy the user draw symbols and how similarly they are conceptual.  Table \ref{tab:ConfusionMatrix} (confusion matrix) shows the types of error in Hs-DB which shows that the system was confused between parallelogram and trapezoid, moon and arch. Those errors were due to users drawing styles as some user may draw a parallelogram as a trapezoid.

>>>>

The system has two main parts the DPSO stroke segmentation and symbol recognition. Each part is evaluated separately. The preprocessing procedures and computation is evaluated using their effect on the segmentation algorithm. These results are reported in section \ref{sec:ResultsDetails}. The effect of number of particles, the error thresholds and various other PSO parameters are investigated in Section \ref{sec:PSO}. %The results presented in Section \ref{sec:ResultsDetails} and \ref{sec:PSO}.

@@

	\caption[Symbols in EL-DB]{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}
\begin{table}
\begin{center}
\scalebox{0.9}{
 \begin{tabular}{|p{5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
 \hline
 & Hs-DB &  EL-DB & LD-DB \\ \hline
No of samples  &  7791 & 2764 & 1859 \\ \hline
No of categories  & 13 & 15 & 8 \\ \hline
Avg. Samples per Category& 600 & 184 & 232 \\\hline 
No of users  & 16 & 7 & 7 \\  \hline
Balanced & Yes&No & No \\ \hline
Splits  & 5 random splits  & 5 random splits  & 5 random splits  \\ \hline
Examples & Figure \ref{fig:symbolSet}  & Figure \ref{fig:ElectSet}  & Figure \ref{fig:LogicSet}   \\ \hline
\end{tabular}
}
\caption[Datasets Comparisons]{Datasets Comparisons} 
\label{tab:datasets}

@@

 The effect of number of particles, the error thresholds and various other parameters was investigated. The result of these tests are shown in Figure \ref{fig:swarmtesting} and \ref{fig:swarmtesting2}. Figure \ref{fig:swarmtesting} shows that as the number of particles increase the \textit{Segmentation Error} value decrease. Similar results for the maximum swarm iterations are shown in Figure \ref{fig:swarmtesting}. Other algorithm parameters like $c_1$,$c_2$ that were mentioned in Section\ref{sec:ParticleSwarmAlgorithm} are tested using similar tests (Figure \ref{fig:swarmparamterw.jpg} and \ref{fig:swarmtesting2}). The final values are for maximum number of iteration = 80 with 15 particles. The final number of particles and maximum swarm iteration used in the system was based trade off between errors achieved versus the computation time.

 \begin{figure}
	\centering		
	 \includegraphics[scale=0.5]{paperImages/swarmAgentTest.eps}
	 	\caption{Segmentation Error Vs. Number of particles}
	 	\label{fig:swarmtesting}
	%\caption{Experiments results :} a)    b) c) 
\end{figure} 
\begin{figure}
	\centering
		\includegraphics{paperImages/swarmIterationTest.eps}
	\caption{Segmentation Error Vs. Number of Swarm iteration}
	\label{fig:swarmIterationTest}
\end{figure}

@@

 The effects of symbol complexity in a dataset were testing in the following experiment. These experiments test how many samples will be required to finally obtain good performance from the recognizer system. In the following experiments, we tested the system using different number of sample per category. 
 Figure \ref{fig:Alg1Ds} and \ref{fig:Alg2Ds} shows that Hs-DB requires more number of sample for training to achieve same result as in other data sets. This is due that it contains less signal and conceptual variation that the other two datasets. Figure \ref{fig:samplesofHS-DB.jpg} shows sample of data collected from one user in Hs-Db it is clear that it has reasonable amount of variation between users but it is limited. Recognizing symbols that contains high variation in drawing style using fewer symbols in training prove the efficiency of our system.
 \begin{figure}
	\centering
		\includegraphics{results/Alg1Ds.eps}
	\caption{AlgS1 on different datasets}
	\label{fig:Alg1Ds}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/Alg2Ds.eps}
	\caption{AlgS2 on different Datasets }
	\label{fig:Alg2Ds}
\end{figure}
 \begin{figure}
	\centering
	\includegraphics[scale=0.5]{results/samplesofHS-DB.jpg.eps}
	\caption[Hs-DB shapes drawn by single user]{Hs-DB shapes drawn by single user \cite{HeloiseBeautification} }
	\label{fig:samplesofHS-DB.jpg}
\end{figure}
  Figure \ref{fig:correct2.jpg} shows examples of correctly recognized symbol using our system. The figure shows that system recognized some hard to recognize example in both EL-DB and DL-DB. An example of symbols that was not correctly recognized are in Figure \ref{fig:erros}. Most of the wrong classifications were due to how messy the user draw symbols and how similarly they are conceptual.  Table \ref{tab:ConfusionMatrix} (confusion matrix) shows the types of error in Hs-DB which shows that the system was confused between parallelogram and trapezoid, moon and arch. Those errors were due to users drawing styles as some user may draw a parallelogram as a trapezoid.
